---
title: "PP"
author: "Emilio Portela Navarro"
date: "2024-05-31"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
library(ggplot2)
ggplot(datos2, aes(x = ESCIDEOL, fill = Voto_Total)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribución de la ideología por partido político",
       x = "Ideología",
       y = "Densidad",
       fill = "Partido político") +
  scale_fill_manual(values = colores_partidos) +
  theme_minimal()
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
